---
title: "EDLD 652 Lab 1"
author: "Chansiri, Wongphothipahan, & Loan"
date: "1/13/2021"
output: html_document
---

Plot 1 is here


Plot 2 is here

```{r}
library(tidyverse)
library(here)
rstats_tweets <- readRDS(here("rstats_tweets.rds"))
```


``````{r}
rstats.with.month<-rstats_tweets %>% 
  mutate(month = lubridate::round_date(rstats_tweets$created_at, unit="month"))
```

```{r}
Plot2.dat<-count(rstats.with.month$month)
```

```{r}
Plot2.dat<-Plot2.dat %>% 
  filter(x < lubridate::as_date("2019-01-01"))
```


```{r}
ggplot(Plot2.dat, aes(x, freq))+ 
  geom_line() +geom_smooth()
```

```{r}
ggplot(Plot2.dat, aes(x, freq)) + 
  geom_line(color="#757575", size = 1) + 
  geom_area(fill = "#6e91f2", alpha = .3)+ 
  geom_smooth(color = "#f500e4", se = F)
```

```{r}
ggplot(Plot2.dat, aes(x, freq)) +geom_line(color="#757575", size = 1)+
  geom_area(fill = "#6e91f2", alpha = .3)+
  geom_smooth(color = "#f500e4", se = F) + 
  labs(x = "Year (data summarized by month)", y = "Number of #stats tweets", title = "Growth of the #rstats hashtag on twitter over time", caption = "Data from Mike Kearny, distributed via #tidytuesday")
```

```{r}
ggplot(Plot2.dat, aes(x, freq)) +
  geom_line(color="#757575", size = 1)+
  geom_area(fill = "#6e91f2", alpha = .3) + 
  geom_smooth(color = "#f500e4", se = F) + 
  labs(x = "Year (data summarized by month)", 
       y = "Number of #stats tweets", 
       title = "Growth of the #rstats hashtag on twitter over time", 
       caption = "Data from Mike Kearny, distributed via #tidytuesday") + 
  theme_minimal()
```




